A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
fixed weird formatting thing I caused
fixed survey response table

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &NUM\\
How many years have you spoken [HIT language]?&NUM\\
How many years have you spoken English?&NUM\\
What country do you live in?&308,079\\
Current location (collected automatically)& 308,079\\
\hline\\
Total assignments& 308,079\\
Total unique workers& 5,271\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.  In total, 308079 translation tasks were completed by 5271 workers over
a period of three and a half months.
20955 synonym tasks were used to judge the submitted translations, and
were completed by an additional 1006 workers.

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\centering
\include{summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &3,480\\
How many years have you spoken [HIT language]?&3,767\\
How many years have you spoken English?&3,840\\
What country do you live in?&3,890\\
Current location (collected automatically)& 5,054\\
\hline\\
Total unique workers& 5,281\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of Turkers with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The task paid \$0.15 for the translation of 10 words.  Each set of 10 words was independently translated by three separate workers.  In total, 308079 translation tasks were completed by 5281 workers over
a period of three and a half months.
20955 synonym tasks were used to judge the submitted translations, and
were completed by an additional 1006 workers.

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\include{summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
